%\thispagestyle{empty}

%\lipsum[1]

I would like to express my deep gratitude to all the people who were present at this important stage of my life and who contributed to the realization of this work. Even those whom I may never have met personally played a key role in the structure that made this project possible.

First of all, I would like to express my sincere gratitude to my beloved family for their unconditional support throughout this journey. In particular, I would like to thank my mother, Ana Maria Capitanio, and my father, Flavio Capitanio, for being a constant source of love and encouragement. I am also grateful to my sister, Raissa Capitanio, for her continued support and encouragement.

In addition, my deepest gratitude extends to my wife, Debora de Lima Wahlus, for her unwavering support and for being by my side throughout the process. Her presence and support have been invaluable.

A special thanks goes to my supervisor, João Paulo Coelho, for giving me the opportunity to do this amazing work. His guidance, knowledge, and incentive were fundamental for the success of this project. I am also grateful to my advisor in Brazil, Juan José Franchini Ferreira, for his constant support and sharing of knowledge.

I would like to express my gratitude to Professor Christian Naaktgeboren, for sharing his knowledge during my studies and being an inspiration as an academic and engineer.

To my home university, the Universidade Tecnológica Federal do Paraná, I express my gratitude for offering me a free and quality education with excellent teachers. Furthermore, I am grateful for the opportunity to participate in the Dual Diplomacy program, which allowed me to expand my academic and cultural horizons.

I would also like to thank my friend Carlos Seiti for his constant support and motivational talks. His quest for personal growth and constant improvement inspires me.

Finally, I would like to express my gratitude to Instituto Politécnico de Bragança for welcoming me to Portugal and to the partner company More, especially Nuno Manuel Pereira Guedes, for their valuable contribution to this project. His collaboration and support were fundamental for the success of this work.

%\vfill
%\pagebreak
%\mbox{}
%\vfill
%\pagebreak
